---
output:
  md_document:
    variant: markdown_github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RegistersClientR

This package doesn't really wrap the
[registers](https://registers.cloudapps.digital/)
[API](https://registers-docs.cloudapps.digital/#api-documentation-for-registers).
Instead, it downloads the 'raw' registers in RSF (Register Serialisation
Format), and parses that.

Registers are authoritative lists of things, built and maintained by the UK
government, for example, the `country` register is a list of countries.

## Installation

```{r, eval = FALSE}
# install.packages("devtools") # if you don't already have devtools installed
devtools::install_github("openregister/RegistersClientR")
```

To install a very early version of the package for running old scripts:

```{r, eval = FALSE}
devtools::install_github("openregister/RegistersClientR",
                         ref = "08c42c95bc65a0cb8131100416a372660b8a1bd5")
```

## Examples

```{r}
library(RegistersClientR)
```

### Download registers

Download a single register.

```{r}
rr_register("country")
```

Download all registers.

```{r}
registers <- rr_registers()
names(registers)
```

By default, the 'beta' ('ready to use') versions of registers are downloaded.
If you need alpha ('open for feedback') registers, use `phase = "alpha")`

### Explore register schema and data

The schema and data are in `$shema` and `$data`.

```{r}
country <- registers$country
country$schema
country$data
```

You probably want to take a snapshot first.  This will take the latest version
of the schema, and the latest version of each record (e.g. the most recent name
of a country)

```{r}
country$schema$custodian
rr_snapshot(country)$schema$custodian
```

Each field of each entry can contain more than one value, if the field has the
property `cardinality = 'n'`.  In this case, the field is a list-column, where
each value is a vector of values.

### Linked registers

Registers link in two ways.

* Via a field with the `"register"` property set in the schema.  This is like a
  foreign/primary key relationship in a relational database.
* Via CURIEs of the form `"prefix:reference"`, where `prefix` is the name of
  a register, and `reference` is a value in the primary field of that register
  (the field with the same name as the register).

```{r}
rr_links(registers$`statistical-geography`)
```

Resolve links with the `rr_resolve_*()` family of functions.  Because links
refer to whole records, whole records are returned in a list-column of data
frames.

If a matching record has multiple entries, every entry is returned in a
multi-row data frame.

If a linking field is `cardinality = 'n'`, a list of data frames is returned.

```{r}
rr_resolve_links(registers$`statistical-geography`, registers)$data
```

You can resolve to only the latest entry of each record by creating a
`registers` object with snapshots.

```{r}
registers_snapshot <- purrr::map(registers, rr_snapshot)
rr_resolve_links(registers$`statistical-geography`, registers_snapshot)$data
```

Plot the links between registers with something like the `ggraph` package.

```{r}
library(tidygraph)
library(ggraph)

registers$`statistical-geography` %>%
  rr_links() %>%
  as_tbl_graph() %>%
  ggraph(layout = "nicely") +
    geom_edge_fan(aes(alpha = ..index..), show.legend = FALSE) +
    geom_edge_loop() +
    geom_node_label(aes(label = name)) +
    theme_void()

edge_arrow <- arrow(length = unit(4, "mm"), type = "closed")
registers %>%
  rr_links() %>%
  dplyr::distinct(from, to, type) %>%
  as_tbl_graph() %>%
  ggraph(layout = "nicely") +
    geom_node_point() +
    geom_edge_fan(aes(colour = type),
                  arrow = edge_arrow,
                  end_cap = circle(2, 'mm')) +
    geom_edge_loop(aes(colour = type),
                   arrow = edge_arrow,
                   end_cap = circle(2, 'mm')) +
    geom_node_label(aes(label = name), repel = TRUE, alpha = .5) +
    theme_void()
```

### Index registers

You can index registers by any column, using CURIE-like syntax.

```{r}
country <- registers$country
rr_index(country, "start-date")
rr_index(country, "end-date")
rr_index(country)
rr_index(rr_register("local-authority-eng"), "local-authority-type")
```
